\documentclass[12pt,a4paper]{article}
\usepackage{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{fancyhdr}

% Document Setup
\title{Half-Yearly Progress Report}
\author{Aandrew Baggio S}
\date{\today}

% Header and Footer
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\cfoot{\thepage} % Set page number in center footer
\renewcommand{\headrulewidth}{0pt} % HEADER LINE REMOVED

% Custom spacing
\setstretch{1.5}

\begin{document}

% Title Page
\begin{titlepage}
    \centering
    \vspace*{2cm}
    \underline{\textbf{\Large Half-Yearly Progress Report for Jul-Nov 2025}}\\\underline{\textbf{\Large Data Sheet for Ph.D Scholars}}
    
    \vspace{2cm}
    \begin{tabular}{ll}
        \textbf{Name:} & Aandrew Baggio S\\
        \textbf{Registration No.:} & EE20D067 (5th Year Survivor)\\
        \textbf{Department:} & Electrical Engineering (EE7)\\
        \textbf{Date for Joining:} & Feb 2, 2021 (A happier time)\\
        \textbf{Specialization:} & Control and Optimization\\
        \textbf{Research Area:} & Synchronization via Spectral Graph Theory\\
        \textbf{Category:} & HTRA (Highly Tired Research Assistant)\\
        \textbf{Guide:} & youtube channels\\
        \textbf{Social Media:} & \textbf{@baggio\_dass} (Instagram)\\
    \end{tabular}
    
    \vfill
    
    \textit{\small *Note: The research details are factual, but the funny parts were generated by Perplexity.}
\end{titlepage}

\section*{Date of DC meetings}

\begin{table}[h]
\centering
\begin{tabular}{|c|p{5cm}|c|}
\hline
\textbf{Description} & \textbf{Event} & \textbf{Date} \\
\hline
1$^{\text{st}}$ DC meeting & Comprehensive Viva (Survival Mode) & Passed somehow\\
\hline
2$^{\text{nd}}$ DC meeting & Research Proposal (Promising the Moon) & Done\\
\hline
3$^{\text{rd}}$ DC meeting & Mid-Term Review (Realizing the Moon is far) & 3.5 Years Mark\\
\hline
4$^{\text{th}}$ DC meeting & Research Colloquium (The "Almost There" Phase) & TBD\\
\hline
Six monthly DC meeting & explaining why $O(n^3)$ is actually fast enough & \begin{tabular}{@{}c@{}}SMD 1: Panic \\ SMD 2: More Panic \\ SMD 3: Acceptance\end{tabular} \\
\hline
Final DC meeting & Synopsis (The Light at the End of the Tunnel) & Please be soon\\
\hline
\end{tabular}
\end{table}

\clearpage

\section*{\centering Details of Course Work}

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{S.No} & \textbf{Course No} & \textbf{Course Title} & \textbf{Sem} & \textbf{Credit} & \textbf{Grade} \\
\hline
\multicolumn{6}{|c|}{\textbf{Core Courses}} \\
\hline
1 & EE5XXX & Linear Algebra (Eigenvalues again?) & 1 & 9 & S \\
\hline
2 & EE6XXX & Nonlinear Systems (Chaos Theory) & 1 & 9 & A \\
\hline
3 & RES101 & Reviewing Reviewer \#2's Comments & 3 & 12 & C- \\
\hline
4 & OPT404 & Optimization (Finding Global Minima of Sleep) & 4 & 9 & B \\
\hline
\multicolumn{6}{|c|}{\textbf{Research "Electives"}} \\
\hline
5 & SOC101 & Instagram Management (@baggio\_dass) & 5 & 10 & S \\
\hline
6 & MAIL99 & Cold Emailing for Postdocs & 5 & 0 & P \\
\hline
\end{tabular}
\end{table}

\vspace{2cm}

\noindent
Signature of Scholar \hfill Signature of Guide

\clearpage

\section*{Contents}

\subsection*{Title of Research Work}
\textbf{A (Purely) Graph-Theoretic Approach to Synchronization of Nonlinear Dynamical Networks (and other things that keep me awake)}
\rule{12cm}{0.4pt}

\subsection*{Problem Definition}
To find a graph-theoretic framework for coupling-strength allocation without using inequality solvers.
\textit{Real Objective:} To graduate before my hair turns completely grey.

\vspace{1cm}

\subsection*{Summary of Work Done before Review}
\begin{enumerate}
    \item Proved that network connectivity matters more than detailed dynamics (and definitely more than my social life).
    \item Reduced complexity to $O(n^3)$ per component. (Still waiting for code to compile).
    \item Analyzed the Lorenz attractor in the chaotic regime ($\sigma=10, r=28$). Coincidentally, my life is also in a chaotic regime.
    \item Drafted the paper for \textit{Systems \& Control Letters}.
\end{enumerate}

\subsection*{Work Done during Review Period}
\begin{enumerate}
    \item Successfully identified "families of directed graphs" where other methods fail but mine works.
    \item Fixed 19 manuscript errors identified by Perplexity.
    \item Spent 3 weeks staring at a "purely graph-theoretic" cycle basis.
    \item Refreshed the Elsevier submission portal 400 times.
\end{enumerate}

\subsection*{Issues Affecting Research Progress}
\begin{itemize}
    \item The coffee machine in ESB 202 is too far from my desk.
    \item Reviewer \#2 thinks my method needs more "rigorous bounds."
    \item Distracted by The Uncertainty Lab's postdoc postings.
\end{itemize}

\subsection*{Future Plans with Proposed Timeline}
\textbf{Month 1:} Resubmit paper to Physica D if SCL rejects it.\\
\textbf{Month 3:} Convince people I know what "Controllability" means.\\
\textbf{Month 6:} Submit Thesis (Inshallah).

\clearpage

\section*{Visible Research Output}

\subsection*{Journals (Under Review/Published)}
\begin{enumerate}
    \item \textbf{A. Baggio S}, G. Arunkumar, \textit{"A (Purely) Graph-Theoretic Approach to Synchronization..."} (Submitted to Systems \& Control Letters). Status: \textit{Under Review (Please be nice).}
\end{enumerate}

\subsection*{Conferences}
\begin{enumerate}
    \item International Conference on "Why does my Code work locally but not on the Server?" (Keynote Speaker).
\end{enumerate}

\clearpage

\section*{Detailed Report}

\subsection*{1. Research Progress}
I have developed a framework that uses only network topology and a single Lipschitz constant. Basically, I replaced complex math with graph theory so I don't have to solve matrix inequalities. It works, it scales to large networks, and it's $O(n^3)$.

\subsection*{2. Technical Contributions}
\begin{itemize}
    \item \textbf{No Solvers Needed:} We allocate coupling strengths constructively.
    \item \textbf{Handling Infeasibility:} Solved synchronization for directed topologies where LMI solvers gave up.
    \item \textbf{Scalability:} We only look at $n-1$ paths. Efficient and elegant (unlike my sleep schedule).
\end{itemize}

\subsection*{3. Future Research Direction}
Moving from synchronization to controllability of nonlinear networks. Also, figuring out how to get a job next year.
As explained in the README that started all of this madness~\cite{baggio2025-readme}, 
most of the humorous commentary was delegated to a language model~\cite{perplexity2025-humor}. 
The more serious mathematical inspiration comes from Strogatz and Bressoud~\cite{strogatz-nonlinear-dynamics,bressoud-radical-real-analysis,bressoud-radical-lebesgue} 
and the usual suspects in spectral graph theory~\cite{chung-spectral-graph-theory}. 

The remaining structure of this document is heavily influenced by food,
YouTube, and Tamil culture~\cite{baggio2025-food-theory,baggio2025-youtube-ref,baggio2025-tamil-culture,baggio2025-iitm-life}.
\vspace{3cm}

\clearpage

\bibliographystyle{ieeetr}
\bibliography{baggio_progress}

\end{document}
